Computational tools for representation theory of affine Lie algebras

### 2009-07-11 AffineLieAlgebras/ACMS2009/article.tex
More on branching
Folding for branching is written

\begin{equation}
  \label{phi-d}
  \Phi _{\frak{a}\subset \frak{g}}=\left\{ \gamma \in P_{\frak{a}}\mid s\left(
      \gamma \right) \neq 0\right\} ;  
\end{equation}
\begin{equation}
  \label{fan-d}
  \prod_{\alpha \in \left( \pi _{\frak{a}}\circ \Delta ^{+}\right) }\left(
    1-e^{-\alpha }\right) ^{\mathrm{{mult}\left( \alpha \right) -{mult}}_{\frak{a%
      }}\mathrm{\left( \alpha \right) }}=-\sum_{\gamma \in \Phi _{\frak{a}\subset 
      \frak{g}}}s\left( \gamma \right) e^{-\gamma }.  
\end{equation}
\begin{equation}
  \label{fan-defined}
  \Gamma _{\frak{a}\subset \frak{g}}=\left\{ \xi -\gamma _{0}|\xi \in \Phi _{%
      \frak{a}\subset \frak{g}}\right\} \setminus \left\{ 0\right\} .
\end{equation}

@@

It is well-known (see for example \cite{wakimoto2001idl}, \cite{kac1990idl}) that characters are Weyl-invariant.
\begin{equation}
  \label{eq:8}
  ch(L^{\omega\mu})=ch(L^{\mu})
\end{equation}
Also Weyl group of the subalgebra is subgroup of Weyl group of algebra $W_{\mathfrak{a}}\subset W_{\mathfrak{g}}$.
Using Weyl-Kac character formula
\begin{equation}
  \label{eq:11}
  ch(L^{\mu})=\frac{\sum_{\omega\in W}\epsilon(\omega)e^{\omega(\mu+\rho)-\rho}}{\prod_{\alpha\in \Delta^{+}}(1-e^{\alpha})^{mult(\alpha)}}
\end{equation}
the equation \eqref{eq:9} can be rewritten as
\begin{equation}
  \label{eq:10}
  \pi_{\mathfrak{a}}(ch L^{\mu}_{\mathfrak{g}})=\frac{\sum_{\nu\in P^{+}_{\mathfrak{a}}}b^{(\mu)}_{\nu} \Psi^{(\nu)}_{\mathfrak{a}}}{R_{\mathfrak{a}}}
\end{equation}
where we have introduced the singular weight elements $\Psi^{(\nu)}_{\mathfrak{a}}=\sum_{\omega\in W_{\mathfrak{a}}}\epsilon(\omega)e^{\omega(\nu+\rho_{\mathfrak{a}})-\rho_{\mathfrak{a}}}$ for $\mathfrak{a}$-modules $L^{\nu}_{\mathfrak{a}}$ and the denominator $R_{\mathfrak{a}}=\prod_{\alpha\in \Delta^{+}_{\mathfrak{a}}}(1-e^{\alpha})^{mult_{\mathfrak{a}}(\alpha)}$.

\section{Details of implementation}
\label{sec:details-implementation}

>>>>

\begin{equation}
  \label{phi-d}
  \Phi _{\frak{a}\subset \frak{g}}=\left\{ \gamma \in P_{\frak{a}}\mid s\left(
      \gamma \right) \neq 0\right\} ;  
\end{equation}
\begin{equation}
  \label{fan-d}
  \prod_{\alpha \in \left( \pi _{\frak{a}}\circ \Delta ^{+}\right) }\left(
    1-e^{-\alpha }\right) ^{\mathrm{{mult}\left( \alpha \right) -{mult}}_{\frak{a%
      }}\mathrm{\left( \alpha \right) }}=-\sum_{\gamma \in \Phi _{\frak{a}\subset 
      \frak{g}}}s\left( \gamma \right) e^{-\gamma }.  
\end{equation}
\begin{equation}
  \label{fan-defined}
  \Gamma_{\frak{a}\subset \frak{g}}=\left\{ \xi -\gamma _{0}|\xi \in \Phi _{%
      \frak{a}\subset \frak{g}}\right\} \setminus \left\{ 0\right\} .
\end{equation}

@@

It is well-known (see for example \cite{wakimoto2001idl}, \cite{kac1990idl}) that characters are Weyl-invariant.
\begin{equation}
  \label{eq:8}
  ch(L^{\omega\mu})=ch(L^{\mu})
\end{equation}
Also Weyl group of the subalgebra is subgroup of Weyl group of algebra $W_{\mathfrak{a}}\subset W_{\mathfrak{g}}$.
Using Weyl-Kac character formula
\begin{equation}
  \label{eq:11}
  ch(L^{\mu})=\frac{\sum_{\omega\in W}\epsilon(\omega)e^{\omega(\mu+\rho)-\rho}}{\prod_{\alpha\in \Delta^{+}}(1-e^{\alpha})^{mult(\alpha)}}
\end{equation}
the equation \eqref{eq:9} can be rewritten as
\begin{equation}
  \label{eq:10}
  \pi_{\mathfrak{a}}(ch L^{\mu}_{\mathfrak{g}})=\frac{\sum_{\nu\in P^{+}_{\mathfrak{a}}}b^{(\mu)}_{\nu} \Psi^{(\nu)}_{\mathfrak{a}}}{R_{\mathfrak{a}}}
\end{equation}
where we have introduced the singular weight elements $\Psi^{(\nu)}_{\mathfrak{a}}=\sum_{\omega\in W_{\mathfrak{a}}}\epsilon(\omega)e^{\omega(\nu+\rho_{\mathfrak{a}})-\rho_{\mathfrak{a}}}$ for $\mathfrak{a}$-modules $L^{\nu}_{\mathfrak{a}}$ and the denominator $R_{\mathfrak{a}}=\prod_{\alpha\in \Delta^{+}_{\mathfrak{a}}}(1-e^{\alpha})^{mult_{\mathfrak{a}}(\alpha)}$. In the paper \cite{ilyin812pbc} following notation was introduced
\begin{equation}
  \label{eq:12}
  \sum_{\nu\in P^{+}_{\mathfrak{a}}}b^{(\mu)}_{\nu} \Psi^{(\nu)}_{\mathfrak{a}}
  =\sum_{\nu\in P^{+}_{\mathfrak{a}}}b^{(\mu)}_{\nu} \sum_{\omega\in W_{\mathfrak{a}}}\epsilon(\omega)e^{\omega(\nu+\rho_{\mathfrak{a}})-\rho_{\mathfrak{a}}}
  \equiv\sum_{\lambda\in P_{\mathfrak{a}}}k_{\lambda}^{(\mu)}e^{\lambda}
\end{equation}
The numbers $k_{\lambda}^{(\mu)}$ are called anomalous branching coefficients and are equal to the multiplicities of the submodules $L^{\nu}_{\mathfrak{a}}$ times the determinants $\epsilon(\omega)$.

Now we can rewrite formula \eqref{eq:10} as
\begin{equation}
  \label{eq:13}
  \pi_{\mathfrak{a}}(ch L^{\mu}_{\mathfrak{g}})=
  \frac{\sum_{\lambda\in P_{\mathfrak{a}}}k_{\lambda}^{(\mu)}e^{\lambda+\rho_{\mathfrak{a}}}}{e^{\rho_{\mathfrak{a}}}R_{\mathfrak{a}}}
\end{equation}
Here we have multiplied the numerator and the denominator by $e^{\rho_{\mathfrak{a}}}$. Now we multiply both sides of equation by ${e^{\rho_{\mathfrak{a}}}R_{\mathfrak{a}}}$.
\begin{equation}
  \label{eq:14}
   \pi_{\mathfrak{a}}(ch L^{\mu}_{\mathfrak{g}})e^{\rho_{\mathfrak{a}}}R_{\mathfrak{a}}=
  \sum_{\lambda\in P_{\mathfrak{a}}}k_{\lambda}^{(\mu)}e^{\lambda+\rho_{\mathfrak{a}}}
\end{equation}
Then left-hand side of equation is anti-invariant under Weyl transformations of group $W_{\mathfrak{a}}$, since the character of $L^{\mu}_{\mathfrak{g}}$ is invariant, projection $\pi_{\mathfrak{a}}$ is orthogonal and $e^{\rho_{\mathfrak{a}}}R_{\mathfrak{a}}$ is anti-invariant ($\omega(e^{\rho_{\mathfrak{a}}}R_{\mathfrak{a}})=\epsilon(\omega)e^{\rho_{\mathfrak{a}}}R_{\mathfrak{a}}$, see \cite{wakimoto2001idl} for the proof). So we have
\begin{equation}
  \label{eq:15}
  \omega\left(\sum_{\lambda\in P_{\mathfrak{a}}}k_{\lambda}^{(\mu)}e^{\lambda+\rho_{\mathfrak{a}}}\right)=
  \epsilon(\omega)\sum_{\lambda\in P_{\mathfrak{a}}}k_{\lambda}^{(\mu)}e^{\lambda+\rho_{\mathfrak{a}}}
\end{equation}
It can be rewritten as
\begin{equation}
  \label{eq:16}
 \sum_{\lambda\in P_{\mathfrak{a}}}k_{\omega^{-1}(\lambda+\rho_{\mathfrak{a}})-\rho_{\mathfrak{a}}}^{(\mu)}e^{\lambda+\rho_{\mathfrak{a}}}=
  \epsilon(\omega)\sum_{\lambda\in P_{\mathfrak{a}}}k_{\lambda}^{(\mu)}e^{\lambda+\rho_{\mathfrak{a}}}
\end{equation}
Then we can equate coefficients of identical exponents
\begin{equation}
  \label{eq:17}
  k_{\lambda}^{(\mu)}=\epsilon(\omega)k_{\omega(\lambda+\rho_{\mathfrak{a}})-\rho_{\mathfrak{a}}}^{(\mu)}
\end{equation}
We see that Weyl symmetry gives us all the values of $k_{\lambda}^{(\mu)}$ from the values inside the shifted by $-\rho_{\mathfrak{a}}$ fundamental Weyl chamber $C_{\mathfrak{a}}-\rho_{\mathfrak{a}}$.

In the paper \cite{ilyin812pbc} following recurrent formula for computation of $k_{\lambda}^{(\mu)}$ was proved
\begin{equation}
  \label{recurrent-relation}
  k_{\lambda }^{\left( \mu \right) }=-\frac{1}{s\left( \gamma _{0}\right) }\left(
\sum_{w\in W}\epsilon \left( w\right) \delta _{\lambda ,\pi _{\frak{a}}\circ
\left( w\circ (\mu +\rho )-\rho \right) +\gamma _{0}}+\sum_{\gamma \in
\Gamma _{\frak{a}\subset \frak{g}}}s\left( \gamma +\gamma _{0}\right) k_{\lambda
+\gamma }^{\left( \mu \right) }\right)   
\end{equation}
Here $k_{\lambda}^{(\mu)}$ is computed as the sum over special set $\Gamma _{\frak{a}\subset \frak{g}}$ \eqref{fan-defined}.

Using relation \eqref{eq:17} we can restrict computation to the shifted by $-\rho_{\mathfrak{a}}$ fundamental Weyl chamber $C_{\mathfrak{a}}-\rho_{\mathfrak{a}}$. Then branching coefficients inside the fundamental Weyl chamber are given by anomalous branching coefficients $b_{\lambda}^{(\mu)}=k_{\lambda}^{(\mu)}\;\mbox{for}\;\lambda\in C_{\mathfrak{a}}$ \cite{ilyin812pbc}.
\section{Details of implementation}
\label{sec:details-implementation}
